### 2021-03-16 README.Rmd
change name of action and add badge to README

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/BrunaLab/HeliconiaDemography/master?urlpath=rstudio) <!-- [![R build status](https://github.com/BrunaLab/HeliconiaDemography/workflows/R-CMD-check/badge.svg)](https://github.com/BrunaLab/HeliconiaDemography/actions) -->

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/BrunaLab/HeliconiaDemography/master?urlpath=rstudio) [![Run Tests](https://github.com/BrunaLab/HeliconiaDemography/actions/workflows/run-testthat.yaml/badge.svg)](https://github.com/BrunaLab/HeliconiaDemography/actions/workflows/run-testthat.yaml)
